---
title: "wk9-homework-lastname-firstname"
author: "Lin Chen"
date: "November 23, 2015"
output: html_document
---

#### 1. Initial GitHub workflow

a. Pat yourselves on the back if you were able to "fork", then "clone" this repo. Maybe massage your brain, too.

b. Re-save this file with your last and first name as well as altering the title of this file.

#### Tips for creating functions

*Use the least possible number of steps. Work line by line, printing out each value as you create the function. Trying to create a function that will solve the whole problem will typically lead to long debugging times because you will not know where you made the mistake.*

#### 2. if-then-else
Create a function `is.a.number()` that takes a single parameter `X` and returns `"Is a number"` if it is a number, `"Is NA"` if it is an `NA` value, and `"I have no clue"` if it is neither a number nor an `NA` value. Use the `is.na()` and `is.numeric()` functions.

```{r}
is.a.number<-function(x) {
    y<-"I have no clue"
    if (is.numeric(x)) {
      y<-"Is a number"}
    if (is.na(x)) {
      y<-"NA"}
    return(y)
}
```

#### 3. primes 
Create a function that when inputting a single prime number between 3 and 100, it will output a `TRUE` or `FALSE` in a `message()`. Insert an error message as if somebody were to insert a number less than 3, greater than 100, or a non-numeric character. (*Please don't insert all of the prime numbers between 3 and 100 into the function...*)

```{r}
number.range.check<-function(x) {
  if (x<3 | x>100| is.character(x)) {
    message("ERROR!")
  } else {
    if (x>=3 & x<=100) {
      message("TRUE")
    } else {
      message("FALSE")
    }
    }
}
```


#### 4. ggplot2

a. Using `ggplot2`, create a function that when inputting a single continuous variable, it will print out a histogram. Include arguments to alter the theme, x-variable label, a title, and a `TRUE` or `FALSE` option to create a density plot.

```{r}
histo.function<-function(data,theme1,xlab1,title1,densityoption) {
  library(ggplot2)
  length<-seq(1,length(data))
  df<-data.frame(data,length)
  m<-ggplot(df,aes(x=data))+geom_histogram()+labs(title=title1,x=xlab1)
  if (densityoption) {
    m<-m+geom_density()
  }
  if (theme1) {
    m<-m+theme_classic()
  }
  return(m)
}
```


b. Similarly, create a function that when inputting two continuous variables, it will print a scatterplot. Additionally, in the console, print the mean and variance of the two variables as well as the coefficient value of the specified x-variable.  Include arguments to alter the title and a `TRUE` or `FALSE` option to include a smoothing method of *lm* aka a simple linear model line in/on the scatterplot.

```{r}
histo2.function<-function(data1,data2,title1,smoothingoption) {
  library(ggplot2)
  df<-data.frame(data1,data2)
  m<-ggplot(df,aes(x=data1,y=data2))+geom_point()+labs(title=title1)
  mean1<-mean(data1)
  mean2<-mean(data2)
  var1<-var(data1)
  var2<-var(data2)
  coeffi<-coef(data1~data2)
  if (smoothingoption) {
    m<-m+geom_smooth()
  }
  return(list(m,"mean of data 1=",mean1, ";","mean of data 2=", mean2,";","variance of data1=",var1,";","variance of data2=", var2, ";","coefficient value of the specified x-variables=", coeffi))
}
```

#### 5. Remaining GitHub workflow

a. Now finish off the workflow of submitting your homework by "committing" the changes locally, "pushing" the changes to YOUR online repo, and finally creating a pull request. 

b. Pat yourselves on the back, again.  You deserved it.
